### 2018-02-11 Writing/Thesis/content/chapter-evaluation.tex

\section{Experimental Setup}

% Gathering data sets from OpenML
how many data sets from OpenML

% Generating base performance data
Performance Values acquired with 5 times MCCV
which (hyper)parameters where used
which timeouts used
why decided to use these algorithms and not others

% How find best version of preference and regression ranker

>>>>

\section{Experimental Setup}
In the following paragraphs, it is briefly summarized under which conditions the experiments which led to the results discussed in the next section where observed. This includes which classifiers and data sets where chosen in the evaluation, what the specifications of the machines the evaluation was executed on where, how the evaluation was carried out, and which specific regression based and preference based implementations where used.

% Which classifiers and data sets used
The classifiers considered for a recommended ranking were the learning algorithms implemented in WEKA that are fit for classification, excluding meta and ensemble methods. The full list of the 22 classifiers can be gathered from Table \ref{tab:bestAlgorithmRanking}. They where all used in their default configurations as specified by WEKA.

datasets

% How base performance data generated
The performance data of the classifiers for the selected data sets was generated on [MACHINE DETAILS]. [TIMEOUT AND HARDWARE ALLOCATION DETAILS]. For each of the classifiers, the predictive accuracy (the percentage of correctly classified instances in the data set) was recorded on each data set by means of five times stratified Monte-Carlo cross validation with a 70/30 split in training and test data. When a timeout occurred, the predictive accuracy was set to 0.

% How rest of the evaluation carried out
All other experiments where carried out on a Windows Machine running Windows 10 Education (version 1709) with a Intel(R) Core(TM) i5-4200U CPU running at 1.60GHz (2.30GHz max) and 12 GB RAM. It is notable that especially the time-related results are to be viewed in regard to this setup. No timeouts where used in this evaluation, and the rankers where evaluated on the training data by means of leave-one-out estimation, that is for the n data sets for which performance values where recorded, they where trained with the meta data - performance examples for n - 1 data sets, and queried for the remaining data set. As n = 448 in this case, the full results are not included in the discussion of the results. They can, however, be found in the supplementary material, offering clues to how each ranker performed in the prediction of a ranking for each of the used data sets, identified by their ID on OpenML.

% How find best version of preference and regression ranker
Furthermore, four alternatives where selected for a regression based and preference based alternative each, to get a general idea of how well the respective approach might be suited for the problem. For the regression based approach, the algorithms chosen where random forest, REPTree, M5P, and linear regression. For all of them, the WEKA implemenation \cite{hall2009weka} was used, and the algorithms where used with the standard hyperparameters set by WEKA. As the preference based ranking falls under the category of label ranking, and in the jPL-framework, which was used for the implementation of the label ranking algorithms and data set representations, only two alternatives for label ranking are implemented \cite{intelligent2017jpl}, the other two alternatives where generated by modifying the hyperparameters. The implemented alternatives are label ranking by pairwise comparison and instance based label ranking. As in early tests it became apparent that the instance based approach might hold more potential, for label ranking by pairwise comparison, only the default configuration dictated by jPL was used. For instance based label ranking, the default configuration, a configuration where the rank aggregation algorithm used by the label ranker was set to Kemeny-Young, and a configuration with Kemeny-Young rank aggregation and the number of neighbors of the base learner of the label ranker, namely k nearest neighbor (kNN), set to the square root of the number of instances in the training data set. In the following section, these eight variants are compared with the baseline and oracle mentioned in the previous section, and among each others.

### 2018-02-11 Writing/Thesis/content/chapter-fundamentals.tex

@@

After having discussed the preliminaries that the theoretical approach of this thesis is built upon, the measures that will be used in the evaluation of the different methods are briefly reviewed. These include means of comparing the predicted rankings with actual rankings as well as a statistic that reveals if an advantage regarding one measure can be viewed as significant.

>>>>

original algorithms selection problem \cite{rice1976algorithm} can be viewed as a learning problem itself

@@

After having discussed the preliminaries that the theoretical approach of this thesis is built upon, how a data set can be split into training and test data to estimate the performance of learning algorithms and the measures that will be used in the evaluation of the different ranking methods are briefly reviewed. These include means of comparing the predicted rankings with actual rankings as well as a statistic that reveals if an advantage regarding one measure can be viewed as significant.

\subsection{Estimation Procedures}

- estimation using cross validation (monte carloMCCV)

- estimation using leave one out

### 2018-02-11 Writing/Thesis/content/chapter-introduction.tex

% Of ML, tasks, classification is important & classifier performances vary across data sets, so it is not easy to just pick one
One of the most prominent machine learning tasks is classification: A class is assigned to an instance, for example clients of a bank may be either deemed creditworthy or not, based on factors like other existing credits or the job of the client. But selecting a fitting classifier for a new data set is difficult, since algorithm performances can vary substantially among data sets, and it is not feasible to simply apply a large number of them to empirically find a good match. For example, on a data set about the electricity prices in the Australian state New South Wales \cite{harris1999splice}, the predictive accuracy for the Multilayer Perceptron\footnote{With standard hyperparameters (L:0.3,M:0.2,N:500,V:0,S:0,E:20,H:a).} is 0.7887 \cite{cachada2017run3}. The predictive accuracy of the Random Forest\footnote{With standart hyperparameters (P:100,I:100,num-slots:1,K:0,M:1.0,V:0.001,S:1).} algorithm on the same data set is 0.9236 \cite{cachada2017run}, a much higher value. On a different data set, with the topic of vehicle silhouettes \cite{siebert1987vehicle}, we get a predictive accuracy of 0.7979 for the Multilayer Perceptron \cite{cachada2017run4}, and 0.7518 for Random Forests \cite{cachada2017run2}, showing an advantage of the former on this data set\footnote{Hyperparameters as above.}. So in each case, one would have picked a different algorithm in order to achieve the best results. In general, this means that for a different data set, a different algorithm might yield the best performance.

>>>>

% Of ML, tasks, classification is important & classifier performances vary across data sets, so it is not easy to just pick one
One of the most prominent machine learning tasks is classification: A class is assigned to an instance, for example clients of a bank may be either deemed creditworthy or not, based on factors like other existing credits or the job of the client. But selecting a fitting classifier for a new data set is difficult, since algorithm performances can vary substantially among data sets, and it is not feasible to simply apply a large number of them to empirically find a good match. For example, on a data set about the electricity prices in the Australian state New South Wales \cite{harris1999splice}, the predictive accuracy for the Multilayer Perceptron\footnote{With standard hyperparameters (L:0.3,M:0.2,N:500,V:0,S:0,E:20,H:a).} is 0.7887 \cite{cachada2017run3}. The predictive accuracy of the Random Forest\footnote{With standart hyperparameters (P:100,I:100,num-slots:1,K:0,M:1.0,V:0.001,S:1).} algorithm on the same data set is 0.9236 \cite{cachada2017run}, a much higher value. On a different data set, with the topic of vehicle silhouettes \cite{siebert1987vehicle}, we get a predictive accuracy of 0.7979 for the Multilayer Perceptron \cite{cachada2017run4}, and 0.7518 for Random Forests \cite{cachada2017run2}, showing an advantage of the former on this data set\footnote{Hyperparameters as above.}. So in each case, one would have picked a different algorithm in order to achieve the best results, and this example just illustrates the choice between two algorithms - in reality, the of available algorithms is much larger. In general, this means that for a different data set, a different algorithm might yield the best performance.

### 2018-02-11 Writing/Thesis/content/chapter-related-work.tex

\section{Predicting Rankings}
%% Ranking

% Could do ranking by using meta-knowledge (avg ranking)
One method of ranking algorithms called average-ranking utilizes meta-knowledge to suggest a ranking for a new data set. The meta-knowledge here consists of recording past performances of classifiers on data sets, and computing the average rank of each classifier over all data sets. Performance measures used are often related to the predictive accuracy of the classifier.

% Could do ranking by evaluating on the spot (active testing)

% Another interesting thing is that both of these could be improved by incorporating time
% Speeding up algorithm selection
\cite{DBLP:journals/ml/AbdulrahmanBRV18}

@@

\begin{figure}
\tikzset{edge from parent/.style={draw,->}}
\begin{tikzpicture}[sibling distance=10em,
  every node/.style = {shape=rectangle, rounded corners,
    draw, align=center}]]
  \node {\textcolor{uniblue}{classify}}
    child { node {...} }
    child { node {\textcolor{uniblue}{classifyWithNN}}
    child { node {...} }
      child { node {\textcolor{uniblue}{buildNN} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN}}
        child { node {...} }
        child { node {...} 
          child { node {...}  }
          child { node {\textcolor{uniaccentblue}{addLayer} \\ ... \\ \textcolor{uniaccentblue}{addLayer} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN} } } } }
    };
\end{tikzpicture}
\caption{An example for how the complex task 'classify' might be broken down by ML-Plan. The figure is loosely adapted from \cite{wever2017automatic}. Nodes containing '...' represent an undefined number of subtrees. \textcolor{uniblue}{Complex tasks} and \textcolor{uniaccentblue}{primitive tasks} are distinguished by their color.}
\label{fig:mltree}
\end{figure}

>>>>

\section{Predicting Rankings}
%% Ranking
% Incorporating times
In contrast to ranking solely based on classifier performances, \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} investigated an approach to extend existing ranking methods by incorporating the time needed for the evaluation of the classifier \cite{DBLP:journals/ml/AbdulrahmanBRV18}. They call this combined measure of accuracy and time A3R, and integrate it into to different ranking approaches.

% Rank aggregation A3R
One of those two approaches is called average-ranking. It utilizes meta knowledge to suggest a ranking of classifiers for a new data sets, which in this case consist of recorded past performances of classifiers on data sets. That means this algorithms aggregates the performances of classifiers on all rankings once and then always recommends the same ranking. The new measures is integrated here by, instead of ordering only according to performance values, the classifiers are ordered according to the combined measure A3R.

% Active testing A3R

% Introduce loss curves and how the measure influences them

@@

\tikzsetnextfilename{MLPlanTasks}
\begin{figure}
\tikzset{edge from parent/.style={draw,->}}
\begin{tikzpicture}[sibling distance=10em,
  every node/.style = {shape=rectangle, rounded corners,
    draw, align=center}]]
  \node {\textcolor{uniblue}{classify}}
    child { node {...} }
    child { node {\textcolor{uniblue}{classifyWithNN}}
    child { node {...} }
      child { node {\textcolor{uniblue}{buildNN} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN}}
        child { node {...} }
        child { node {...} 
          child { node {...}  }
          child { node {\textcolor{uniaccentblue}{addLayer} \\ ... \\ \textcolor{uniaccentblue}{addLayer} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN} } } } }
    };
\end{tikzpicture}
\caption{An example for how the complex task 'classify' might be broken down by ML-Plan. The figure is loosely adapted from \cite{wever2017automatic}. Nodes containing '...' represent an undefined number of subtrees. \textcolor{uniblue}{Complex tasks} and \textcolor{uniaccentblue}{primitive tasks} are distinguished by their color.}
\label{fig:mltree}
\end{figure}
